\begin{progprob}
    Suppose you are trying to remove outliers from a data set consisting of
    points in $\mathbb R^d$. One of the simplest approaches is to remove points
    that are in ``sparse'' regions -- that is, points that don't have many
    other points close by. To do this, we might calculate the distance from a
    point to it's $k$th closest neighbor. If this distance is above some
    threshold, we consider the point an outlier.

    More generally, the task of finding the distance from a query point to its
    $k$th closest ``neighbor'' is a common one in data science and machine
    learning.
    Here, we'll consider the 1-dimensional version of the problem of
    finding $k$th neighbor distance. In a file named \python{knn_distance.py},
    write a function named \python{knn_distance(arr, q, k)} that returns a
    pair of two things:

    \begin{itemize}
        \item the distance between \python{q} and the $k$th closest point to \python{q}
            in \python{arr};
        \item the $k$th closest point to \python{q} in \python{arr} itself
    \end{itemize}

    The query point \python{q} does not need to be in
    \python{arr}. For simplicity, \python{arr} will be a Python list of numbers,
    and \python{q} will be a number. \python{k} should start counting at one,
    so that \python{knn_distance(arr, q, 1)} returns the distance between
    \python{q} and the point in \python{arr} closest to \python{q}. Your
    approach should have an expected time of $\Theta(n)$, where $n$ is the
    size of the input list. Your function may modify \python{arr}. In cases
    of a tie, the point you return is arbitrary (though the distance is not).
    Your code can assume that $k$ will be $\leq \python{len(arr)}$.

    Example:
    \begin{minted}[autogobble]{python}
        >>> knn_distance([3, 10, 52, 15], 19, 1)
        (4, 15)
        >>> knn_distance([3, 10, 52, 15,], 19, 2)
        (9, 10)
        >>> knn_distance([3, 10, 52, 15], 19, 3)
        (16, 3)
    \end{minted}

    As this is a programming problem, submit your code to the Gradescope
    autograder.

    \begin{soln}
        The idea is to compute the distance from \python{q} to all of the points
        in \python{arr} in $\Theta(n)$ time, then use quickselect to find the
        $k$th order statistic in $\Theta(n)$ expected time. The tricky part is
        recovering the $k$th point from the $k$th distance. You could loop back
        through the distances searching for the index at which the $k$th
        distance occurs, then use this to index into \python{arr}; essentially,
        a linear search. This would still be linear time, but there's an
        approach that you might consider a little cleaner: instead of doing
        quickselect on the distances alone, run quickselect on tuples of
        distance/point pairs. This solution is shown below:

        \inputminted{python}{\thisdir/include-solution/knn_distance.py}
    \end{soln}
\end{progprob}
