\begin{prob}
    In each of the problems below state the best case and worst case time
    complexities of the given piece of code using asymptotic notation. Note that
    some algorithms may have the same best case and worst case time complexities. If
    the best and worst case complexities \emph{are} different, identify which
    inputs result in the best case and worst case. You do not otherwise need to show your work for
    this problem.

    \emph{Example Algorithm:} \python{linear_search} as given in lecture. 

    \emph{Example Solution:}
    Best case: $\Theta(1)$, when the target is the first element of the array.
    Worst case: $\Theta(n)$, when the target is not in the array.

    \begin{subprobset}
        \begin{subprob}
            \inputminted{python}{\thisdir/include/part_a.py} 

            \begin{soln}
                Best case: $\Theta(1)$, when \python{data[0,0] == 42}.

                Worst case: $\Theta(n^2)$, when \python{42} is not in the array.
            \end{soln}
        \end{subprob}

        \begin{subprob}
            \inputminted{python}{\thisdir/include/part_b.py}
            

            \begin{soln}
                Best case: 
                    $\Theta(n)$.
                    This occurs when the input list is sorted in descending order.

                Worst case: 
                    $\Theta(n^2)$. This occurs when the input list is sorted in ascending order.
            \end{soln}
        \end{subprob}

        \begin{subprob}
            \inputminted{python}{\thisdir/include/part_c.py} 
            

            \begin{soln}
                Best case: $\Theta(n)$, when the first element of the array is a median.

                Worst case: $\Theta(n^2)$, when the first $n-1$ elements are not medians, and the last element of the array is the median.
            \end{soln}
        \end{subprob}

        \begin{subprob}
            \inputminted{python}{\thisdir/include/part_d.py} 
            

            \begin{soln}
                The best case is $\Theta(n)$, while the worst case is $\Theta(n^2)$.

                In the worst case, the mode is at the very end of the list, as in 
                \python{[5, 1, 2, 7, 9, 9]}. The outer loop iterates $n$ times, and the
                inner loop does $\Theta(n)$ work per iteration for a total of $\Theta(n^2)$.

                In the best case, the mode is the first element of the list, as in, for instance
                $\python{[1, 5, 8, 2, 1, 1, 1]}$. The mode will be discovered on the very
                first iteration of the outer loop, but the inner loop will still take $\Theta(n)$
                time, for a total of $\Theta(n)$.
            \end{soln}
        \end{subprob}


        \begin{subprob}
            \inputminted{python}{\thisdir/include/part_e.py} 
            

            \begin{soln}
                Best case: $\Theta(n)$. This occurs when the median is the first element of the array,
                as then \python{median} takes $\Theta(n)$ and \python{linear_search} takes $\Theta(1)$,
                for a total of $\Theta(n)$.

                Worst case: $\Theta(n^2)$. This occurs when the median is the last element of the
                array. In this situation, \python{median} takes $\Theta(n^2)$ time and \python{linear_search}
                takes $\Theta(n)$ time, for a total of $\Theta(n^2)$ time.
            \end{soln}
        \end{subprob}

    \end{subprobset}


\end{prob}
