%% tags: [sorted structure]
%% source: 2023-fa-redemption_midterm_01
\begin{prob}
    A \emph{rotated sorted array} is an array that is the result of taking a sorted array
    and moving a contiguous section from the front of the array to the back of the array.
    For example, the array \mintinline{python}{[5, 6, 7, 1, 2, 3, 4]} is a rotated sorted array: it
    is the result of taking the sorted array \mintinline{python}{[1, 2, 3, 4, 5, 6, 7]} and moving
    the first 4 elements, \mintinline{python}{[1, 2, 3, 4]}, to the back of the array. Sorted
    arrays are also rotated sorted arrays, technically speaking, since you can
    think of a sorted array as the result of taking the sorted array and moving
    the first 0 elements to the back.

    The function below attempts to find the value of the minimum element in a
    rotated sorted array. It is given the array \mintinline{python}{arr} and the indices
    \mintinline{python}{start} and \mintinline{python}{stop} which indicate the range of the array that
    should be searched. One line in the function has been left blank.


    \begin{minted}[autogobble]{python}
        import math
        def find_minimum_in_rotated_sorted(arr, start, stop):
            """
            Searches arr[start:stop] for the smallest element.
            Assumes arr is a rotated sorted array.
            """
            if stop < start:
                return arr[0]

            if stop == start:
                return arr[start]

            mid = (start + stop) // 2

            if ________________:
                return arr[mid + 1]

            if arr[start] < arr[mid]:
                return find_minimum_in_rotated_sorted(arr, mid, stop)
            else:
                return find_minimum_in_rotated_sorted(arr, start, mid - 1)
    \end{minted}

    What should be filled in the blank line to make this function work correctly?

    \begin{choices}
        \choice \mintinline{python}{arr[middle] > arr[stop-1]}
        \choice \mintinline{python}{arr[middle] < arr[stop-1]}
        \choice \mintinline{python}{arr[middle] > arr[start]}
        \choice \mintinline{python}{arr[middle] < arr[start]}
        \correctchoice \mintinline{python}{arr[middle] > arr[middle+1]}
        \choice \mintinline{python}{arr[middle] < arr[middle+1]}
    \end{choices}

    \begin{soln}
        5th option: \mintinline{python}{arr[middle] > arr[middle+1]}
    \end{soln}

\end{prob}
