%% source: 2023-sp-midterm_02
%% tags: [breadth first search, aggregate analysis]
\begin{prob}
    Consider the code below, which is a modification of the code for
    \mintinline{python}{bfs} given in lecture:

    \inputminted{python}{./code.py}

    Notice the two new lines; these lines print all node statuses any time that
    an undiscovered node has been found.

    What is the time complexity of this modified \mintinline{python}{modified_full_bfs}?
    State your answer in asymptotic notation in terms of the number of nodes,
    $|V|$, and the number of edges, $|E|$. You may assume that the graph is
    represented using an adjacency list, and that it is connected.

    \begin{soln}
        $\Theta(V^2)$.

        First, the newly-added code (the \mintinline{python}{for z in graph.nodes} loop),
        takes $\Theta(V)$ time each time the loop is encountered. The crux is: how many
        times is that loop encountered?

        This loop is encountered every time we add a node to the queue (except
        for the root node, which we add to the queue right at the beginning of
        BFS). Since this is a connected graph, each node will get added to the
        pending queue exactly once, meaning that this new code is encountered
        \emph{exactly} $V-1$ times (the $-1$ is subtracting the root node; the
        loop isn't encountered when we change it to pending).

        Since the new code takes $\Theta(V)$ time each time it's encountered,
        and since it's encountered $\Theta(V)$ times, the total time complexity of
        the loop is $\Theta(V^2)$.

        You might wonder why the time complexity isn't $\Theta(VE)$, since the
        new code is within the loop that ``explores'' each edge in the graph,
        and we know that it makes a total of $2|E|$ iterations when the graph
        is undirected. This is true, but recognize that the new code only
        executes when the \mintinline{python}{if}-statement before it is \mintinline{python}{True}, and
        this will happen on only a \emph{subset} of the $2|E|$ iterations. In
        fact, it will happen exactly $|V|-1$ times, as we argued above.
    \end{soln}

\end{prob}
